Pillar 2 - Topic Modeling

### 2019-02-13 Pillar 2 - Topic Modeling.Rmd

## Ideal Number of Topics

```{r LDA number topics, eval = FALSE}
result <- FindTopicsNumber(

  d_description_cast,
  topics = seq(from = 20, to = 150, by = 5),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = list(seed = 123),
  mc.cores = 1L,
  verbose = TRUE

>>>>

## Ideal Number of Topics (RUN ON UM COMPUTER)

```{r LDA number topics, eval = FALSE}

my_control <- list(

  nstart = 10,
  seed   = 1 : 10,
  best   = TRUE,

  burnin = 500
  iter   = 2000,
  thin   = 100

result <- FindTopicsNumber(

  d_description_cast,
  topics = seq(from = 20, to = 150, by = 5),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = my_control,
  mc.cores = 1L
